\documentclass[oneside,11pt]{amsart}
\usepackage[utf8]{inputenc}%
\usepackage[english]{babel}%
\usepackage{amsmath,amssymb,amsthm,amsfonts}%
\usepackage[unicode]{hyperref}%
\usepackage{mathrsfs,bbm}%
\usepackage{paralist}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\newcolumntype{L}[1]{>{\small\raggedright\arraybackslash}m{#1}}
\newcolumntype{T}[1]{>{\footnotesize\raggedright\arraybackslash}m{#1}}
\usepackage{stmaryrd}%
%\usepackage{refcheck}
\usepackage{graphicx}
\usepackage[DIV14]{typearea}
\usepackage{multicol,tikz}
\usepackage{datetime}
\usepackage{cleveref}

\usepackage[shadow]{todonotes}

\usepackage{etoolbox}
\patchcmd{\section}{\scshape}{\Large\itshape\bfseries}{}{}

\usepackage{caption}
\captionsetup{labelformat=empty,labelsep=none}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=green!60!black
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\synctex=1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\score}[1]{\textit{#1}\addtocounter{totalscore}{#1}}
\newcommand{\razdel}[1]{\smallskip\underline{\textbf{#1:}}\smallskip}

\newcommand{\note}[1]{{\sf{}\color{blue}(#1)}}

\begin{document}

\title[MATH 3340: COMPLEX VARIABLES WITH APPLICATIONS]{MATH 3340: COMPLEX VARIABLES WITH APPLICATIONS}
\author{Leonid Petrov\\Spring 2020}
\date{Compiled on \today, \currenttime{} (in whatever timezone I was at that time).\\An up to date syllabus is always on \texttt{GitHub} at \url{https://github.com/lenis2000/Syllabi/blob/master/Syllabus_3340_s20.pdf}. For direct PDF download use \href{https://github.com/lenis2000/Syllabi/raw/master/Syllabus_3340_s20.pdf}{\texttt{this link}}.
	\LaTeX{} source with \textit{changes} to the syllabus is \href{https://github.com/lenis2000/Syllabi/blob/master/Syllabus_3340_s20.tex}{\texttt{here}}
(click ``History'').
\\Note that this PDF has green clickable links.}
\maketitle



\subsection*{Prerequisites}

Good command of single and multivariable calculus at the level of MATH 1310, 1320, and 2310.

\section{Necessary information}
\bigskip

\textbf{Class times:}   TuTh 12:30PM - 1:45PM in
\emph{New Cabell 309}

\medskip


\textbf{Exams:} Please do not make travel plans which conflict
with the first midterm or the final exam.
\begin{itemize}
	\item \textbf{Midterm 1:} In-class on Thursday, February 6 (class time, New Cabell 309).
	\item \textbf{Midterm 2:} In-class on Tuesday, April 7 (class time, New Cabell 309).
	\item \textbf{Final exam:} Tuesday, May 5, 2-5 (New Cabell 309).
\end{itemize}

\medskip

\textbf{Instructor:} Leonid Petrov
\medskip

\textbf{Email:} \email{petrov@virginia.edu} or \email{lenia.petrov@gmail.com}
\medskip

\textbf{Office:} 209 Kerchof Hall
\medskip

\textbf{Office hours:}
The default times I am in office are Tuesdays and Thursdays, 9:30-10:30,
except the weeks when I'm \href{https://lpetrov.cc/2019/05/travel-2020/}{\texttt{traveling}}.

You are welcome to make an appointment and meet outside the usual office hours. 
For this, please use the online tool located at
\url{https://lpetrov.cc/teaching/}. (I am automatically available during office hours --- 
and you cannot schedule appointments online for those times.)
You can make as 
many appointments as you want.

\medskip

\textbf{Course webpage:}
I will set up a collab page for homework submissions and course materials.

\section{Course materials}


\section{Assessing your learning}

\subsection{Homework}













\section{Policies}

\subsection{Laptops and smartphones}

Please do not use laptops and smartphones during the class.
You won't need them to participate in the discussions, but they may easily distract
you or other students (or me!). If you \emph{absolutely} must use a laptop
(for typing up the lecture notes), please sit in the back row.

\subsection{Late/make up work} Each assignment will have due date and time.
Late assignments are not accepted. There will also be no make ups for the midterm tests and the final exam.
However, if you have special needs, emergency, or unavoidable conflicts, please
let me know as soon as possible, so we can arrange a workaround.

\subsection{Honor Code} The University of Virginia Honor Code applies to this
class and is taken seriously. Collaboration on homework
assignments is allowed within the bounds discussed above
in the corresponding section.
Any honor code violations will be referred to the
Honor Committee.

\subsection{Special needs}

All students with special needs requiring accommodations should present the
appropriate paperwork from the Student Disability Access Center (SDAC). It is
the student's responsibility to present this paperwork in a timely fashion and
follow up with the instructor about the accommodations being offered.
Accommodations for test-taking (e.g., extended time) should be arranged at
least 5 business days before an exam.




\end{document}
